---
title: "HW2_template"
author: "G3-Pedram Jahangiry"
date: "2/1/2021"
output:
  word_document: default
  pdf_document: default
---

```{r include=FALSE}
library(wooldridge)
library(dplyr)
```


# R crash course 



this is test. What is the average weight in mtcars data. 

```{r, comment=NA}
mean(mtcars$wt)
```

so here is the average weight: `r round(mean(mtcars$wt),2) `.


------------ 

another test: 

let's type the regression equation: $y= \beta_0 + \beta_1 x_1 + \epsilon$

Now let's put it in the center: $$y= \beta_0 + \beta_1 x_1 + \epsilon$$

----- 

another fun test: 
Let's import a complicated formula into markdown using mathpix: 


$$
\widetilde{\beta}_{1}=\beta_{1}+\left(n^{-1} \sum_{i=1}^{n}\left(z_{i}-\bar{z}\right) u_{i}\right) /\left(n^{-1} \sum_{i=1}^{n}\left(z_{i}-\bar{z}\right) x_{i}\right)
$$


## Question 1

Replicate the following vector of numbers using seq() function and call it **v1**.

```{r, comment=NA}

v1 <- seq(1,17,4)
v1
```


## Question 2 



## Question 3
Assign the dataframe mtcars from the built-in datasets in R to a new dataframe
and call it df. Show the first 10 rows of your dataframs.

```{r, comment=NA}
df<- mtcars
head(df,10)

```


--------------


# computer exercise

## Question 4 

### (i)

What is percentage of the men in the sample report abusing alcohol?

```{r, comment=NA}
df <- alcohol
summary(df$abuse)
```

from the summary table above,  9.917% of men are alcohol abusers in this data set. 

or alternatively the number is `r round(prop.table(table(df$abuse)),3)[2]`



























