---
title: "Using Stargazer to generate cleaner regression tables in R"
author: "Prof. Pedram Jahangiry"
date: "null"
output:
  word_document: default
  pdf_document: default
  html_document:
    df_print: paged
---

---------

```{r include=FALSE}
library(stargazer)
library(wooldridge)
```


```{r, comment=NA}

reg <- lm ( salary ~ roe , ceosal1   )
stargazer(reg, type="text")


```

\newpage

You can put multiple regression results in one table as well: 


```{r, comment=NA}

reg_log <- lm ( log(salary) ~ roe , ceosal1   )
stargazer(reg, reg_log, type="text")


```


--- 


Here are some useful equations for your HW4: 

1. You can write a math eaution and put it in the middle of the page by using two dollar signs: 
$$kids = \beta_0 + \beta_1 educ + u $$

2. Here are some other examples: 
$$E(u|inc) = E(\sqrt{inc} * e|inc) = (\sqrt{inc})E(e|inc)$$ 

$$var(u|inc)= var(\sqrt{inc}. e | u) = \sqrt{inc}^2 var(e|inc) = inc * var(e) = inc * \sigma^2_e$$


$$\widehat{\textit{prate}} = \hat{\beta_0} + \hat{\beta_1}\textit{mrate}$$

3. In-line math equations by using one dollar sign. Example: Since we are working with a level-log model, we know that $\Delta y = (\beta_1/100)\% \Delta x$.



4. writing a regression model in two lines: 
$$\widehat{\textit{math12}} = \hat{\beta_0} + \hat{\beta_1}\textit{read}12$$ 
$$n = ?, R^2 = ?$$












